---
title: "McCall Lab Theme"
author: "Zachary Brehm"
output: github_document
---

## Installation

This package can be installed using devtools.

```r
devtools::install_github("zachbrehm/ggmccalllab")
```

## Introduction

This package is currently in development. This package is intended to provide an
easily deployable color palette and theme for ggplot2 for use by students in the
McCall Lab in the Department of Biostatistics at University of Rochester. The 
palettes in this package are all intended to be color blindy friendly. 


As of right now only one color palette is available, supporting up to 8 colors. 
This palette was adapted by Martin Krzywinski from [Points of view: Color Blindness](https://www.nature.com/articles/nmeth.1618) by Bang Wong.
Further updates to this package will include the remaining palettes displayed on
[Martin's own website](http://mkweb.bcgsc.ca/colorblind/palettes.mhtml#page-container).

```{r include=FALSE}
README <- TRUE
```

```{r readme, child = "vignettes/ggmccalllab.Rmd"}
```

