---
title: "McCall Lab Theme"
author: "Zachary Brehm"
output: github_document
---

## Installation

This package can be installed using devtools.

```r
devtools::install_github("zachbrehm/ggmccalllab")
```

## Introduction

This package is currently in development. This package is intended to provide an
easily deployable color palette and theme for ggplot2 for use by students in the
McCall Lab in the Department of Biostatistics at University of Rochester. The 
palettes in this package are all intended to be color blindy friendly. 

Supports color palettes with 8, 12, 15, or 48 color options. 
These palettes were adapted by [Martin Krzywinski](http://mkweb.bcgsc.ca/colorblind/palettes.mhtml#page-container), of which the 8 color palette was adapted from [Points of view: Color Blindness](https://www.nature.com/articles/nmeth.1618) by Bang Wong.
Further updates to this package will include the remaining palettes displayed on.

```{r include=FALSE}
README <- TRUE
```

```{r readme, child = "vignettes/ggmccalllab.Rmd", out.dir = here::here("man", "figures")}
```

